---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "100%", 
  eval = FALSE
)
```

# metapip

<!-- badges: start -->

<!-- badges: end -->

The goal of `{metapip}` is to provide the user with a set of functions that allow him/her to work efficiently with all the PIP R packages. The technical world of PIP consist of several packages that interact to each to load, format, modify, and estimate data for the PIP system. Given that the number of packages has increased over time, it was necessary to create a meta package whose only objective is the proper management of all the other PIP packages.

`{metapip}` is highly inspired by the [{tidyverse}](https://github.com/tidyverse/tidyverse), so that some of its functions are just a simple refactoring of the `{tidyverse}` functions. All the credit, then, goes to the Tidyerse team. Thank you!

In addition to the basic functionality of attaching and installing PIP-related R packages, `{metapip}` also works as the manager of those packages in your working environment such that you are always working with the right version of any of the PIP packages.

## Core packages

The core PIP R packages are

-   pipapi
-   pipaux
-   pipload
-   wbpip
-   pipfun
-   pipdata
-   pipr

## Installation

You can install the development version of metapip from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("PIP-Technical-Team/metapip")
```

## Functions and it's usage in metapip

```{r setup}
library(metapip)
```

Since `metapip` works with Github API, you need to make sure that your GitHub credentials are properly set in you R environment. The best way to do so is using the `{gitcreds}` package. You may find a simple explanation about how you can generate a token for yourself and set it up [here](https://happygitwithr.com/https-pat#tldr).

You can check if your credentials are properly set by running the following command.
```{r check-credentials}
check_github_token() |> 
  print()
```

Let us now go through the functions in metapip.

1.  `get_branches()`

    This function as the name suggests gives you the available branches for a particular pip package on GitHub. It will display in the console the available branches.

```{r}
get_branches("pipr")   

#── These are available branches for pipr package:  
#• 29-website-formatting
#• 61_global_end
#• DEV
#• add_retry
#• default_options
#• fix_popshare
#• gh-pages
#• httr2
#• main
#• test
```

At the same time it also returns the branch name as character vector invisibly.

```{r}
out <- get_branches("pipr")

#── These are available branches for pipr package:  
#• 29-website-formatting
#• 61_global_end
#• DEV
#• add_retry
#• default_options
#• fix_popshare
#• gh-pages
#• httr2
#• main
#• test

out
#[1] "29-website-formatting" "61_global_end"         "DEV"                   "add_retry"            
#[5] "default_options"       "fix_popshare"          "gh-pages"              "httr2"                
#[9] "main"                  "test"                 
```

There is an argument called `display` which is set as `TRUE` by default. This argument controls if you want to show the branch names in the console or not.

```{r}
out <- get_branches("pipr", display = FALSE)  
out
#[1] "29-website-formatting" "61_global_end"         "DEV"                   "add_retry"            
#[5] "default_options"       "fix_popshare"          "gh-pages"              "httr2"                
#[9] "main"                  "test"                 
```

2.  `install_branch()`

    This installs a specific branch for a particular package.

```{r, eval=FALSE}
install_branch(package = "wbpip", branch = "DEV")
```

The above command will install `DEV` branch of `wbpip` package.

3.  `get_branch_info()`

This function will give you information of a particular branch in a package. For example, when was last commit done on this branch and by whom.

```{r}
get_branch_info(package = "pipr", branch = "DEV")

#  package branch_name last_commit_author_name     last_update_time
#1    pipr         DEV               Tony Fujs 2023-09-04T13:06:47Z
```

You may pass more than one branch names.

```{r}
get_branch_info(package = "wbpip", branch = c("PROD", "QA"))

#  package branch_name last_commit_author_name     last_update_time
#1   wbpip        PROD               Tony Fujs 2023-09-20T08:02:24Z
#2   wbpip          QA                tonyfujs 2023-07-14T08:50:33Z
```

4.  `install_latest_branch()`

This function installs the packages from the branch which was last updated i.e the latest branch.

If you pass no arguments to it, it will install latest branch for all pip core R packages. However, you can also restrict it to only a few packages as well.

```{r, eval=FALSE}
install_latest_branch()
install_latest_branch(c("pipfun", "pipapi"))
```

5.  `core_metadata()`

Get metadata information about pip packages.

```{r}
out <- core_metadata()
out <- core_metadata(c("pipapi", "wbpip"))
```

6.  `install_all_packages()`

Install one or more core packages from a specific branch. If you have fresh installation of R then running `install_all_packages()` would set you up with all pip packages.

```{r, eval=FALSE}
install_all_packages(branch = "test")
install_all_packages(c("pipapi", "wbpip"), "test")
```
