---
title: "metapip in package development"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{metapip in package development}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
 # devtools::load_all(".")
library(metapip)
```


## metapip: Managing PIP Ecosystem Packages for Development

The `metapip` package is designed to make it easy to manage all the packages in the PIP ecosystem. This is especially useful for package development, as the PIP packages depend on each other—most notably, like `pipfun`, which provides shared utilities. Coordinating branches and versions across these packages is essential for a smooth development workflow.

## Default and Custom Branches

To use the most recent version of a package, it's important to know which branch is considered the default for each package. By default, the branch is available with `get_default_branch()`, 

```{r}
get_default_branch()
```


and you can modify it with `set_default_branch()`. For example:

```r
set_default_branch("DEV")
```

However, not all packages' most recent versions are available in the same branch. Packages that do not use the default branch are tracked as "custom branches." You can see these with `get_custom_branch()`:

```{r}
get_custom_branch()
```

## Inspecting and Modifying Branch Assignments

To see all PIP ecosystem packages and their currently assigned branches, use `get_current_branches()`. To get the branch for a specific package, use `get_package_current_branch(package)`. For example:

```{r}
get_current_branches()
get_package_current_branch("pipdata")
```

If you need to change the working branch for any package, use `set_custom_branch()`. For example, to set the `pipdata` package to use the `main` branch and `pipapi` to use `DEV_v3`:

```{r}
set_custom_branch(pipdata = 'main', pipapi = 'DEV_v3')
```

## Listing Core Packages

To get a list of all core PIP packages, use:

```{r}
get_core_pagkages()
```

## Package Development Workflow
When developing a PIP package, it is important to ensure you are using the most recent versions of all other PIP ecosystem packages, each on their appropriate default branch. Typically, you can achieve this by running `metapip::update_pip_packages()`, which updates all core PIP packages except the one you are currently developing.

If you want to both update and attach (i.e., load with `library()`) the PIP packages, use `metapip::init_metapip()`. Both functions automatically detect your current working directory and exclude the package you are developing from updates and attachment.

This behavior is managed by the `get_core_pagkages()` function. By default, it returns all core PIP packages. However, when called with `exclude = NA`, it checks if your working directory is a PIP package and excludes it from the list.

For example, if you are working on the `pipapi` package, `get_core_pagkages(exclude = NA)` will return all core packages except `pipapi`. This ensures you do not accidentally update or reload the package you are actively developing. The following explains the logic behind the process. **Do NOT use this in your code**.


```{r}
# the same as get_core_pagkages() because the working directory 
# is not a PIP package
get_core_pagkages(exclude = NA)

withr::with_dir(
  # Change working directory to fake pipapi
  fs::path_temp() |> 
  fs::path("pipapi") |> 
  fs::dir_create(),
  
  # Since the working directory is a PIP package, 
  # it will be excluded 
  get_core_pagkages(NA))

```

