---
title: "metapip in Package Development"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{metapip in Package Development}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(metapip)
```

## Overview

When developing a PIP package (e.g., `pipapi`, `wbpip`), you need the other
PIP ecosystem packages available at their correct versions. `metapip`
automatically detects when you're working inside a PIP package directory and
excludes it from updates, so you never accidentally overwrite the code you're
actively developing.

## Default and Custom Branches

The global default branch:

```{r}
get_default_branch()
```

Per-package overrides:

```{r}
get_custom_branch()
```

Change the global default:

```r
set_default_branch("DEV")
```

## Inspecting Branch Assignments

See all current assignments:

```{r}
get_current_branches()
```

Get the branch for a single package:

```{r}
get_package_current_branch("pipdata")
```

## Setting Custom Branches

Override individual packages:

```{r}
set_custom_branch(pipdata = "main", pipapi = "DEV_v3")
```

## Listing Core Packages

```{r}
get_core_pagkages()
```

## Auto-Exclusion Logic

When called with `exclude = NA` (the default), `get_core_pagkages()`
automatically detects if your working directory is a PIP package and
excludes it. This is what `init_metapip()` and `update_pip_packages()` use
internally.

```{r}
# Current directory is not a PIP package
get_core_pagkages(exclude = NA)
```

```{r}
# Simulate working inside pipapi
pipapi_dir <- file.path(tempdir(), "pipapi")
dir.create(pipapi_dir, recursive = TRUE, showWarnings = FALSE)
withr::with_dir(
  pipapi_dir,
  print(get_core_pagkages(NA))
)
```

## Package Development Workflow

1. Navigate to your package directory (e.g., `~/repos/pipapi`).
2. Run `update_pip_packages()` -- all core packages **except** `pipapi` are
   updated to their configured branch HEADs.
3. Run `init_metapip()` -- all core packages **except** `pipapi` are installed
   (if outdated) and attached.
4. Develop your package with the correct dependency versions.
5. When done, run `pip_snapshot()` from a neutral directory to update the team
   lock.