---
title: "Branch Configuration and Options"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Branch Configuration and Options}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteDepends{metapip}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
library(metapip)
knitr::opts_chunk$set(eval = FALSE)
```

## Background

Many `metapip` functions accept a `branch` argument. This vignette explains
the three-level priority system for resolving branch names and how to
configure it.

## Branch Resolution Priority

Branch names are resolved in this order (highest priority first):

### Level 1: Explicit argument

Pass `branch` directly to any function that accepts it:

```{r}
get_branch_info(package = "pipapi", branch = "DEV")
```

This always wins, regardless of any option settings.

### Level 2: Per-package custom branch

Use `set_custom_branch()` to override specific packages:

```{r}
set_custom_branch(pipr = "main", pipapi = "DEV_v3")
```

This sets `options(metapip.custom_branch = list(pipr_branch = "main",
pipapi_branch = "DEV_v3"))` behind the scenes. Now:

```{r}
get_branch_info(package = "pipapi")  # Uses "DEV_v3"
```

### Level 3: Global default branch

If neither an explicit argument nor a custom branch is set, the global
default is used:

```{r}
get_default_branch()  # Returns "PROD" by default
```

This comes from `options(metapip.default_branch)`.

## Zero-Configuration Defaults

When `metapip` loads, it ships with sensible defaults:

```{r}
metapip_default_options <- list(
  metapip.default_branch = "PROD",
  metapip.custom_branch = list(
    pipapi_branch = "DEV",
    pipfaker_branch = "main",
    wbpip_branch = "DEV",
    pipster_branch = "DEV"
  )
)
```

So out of the box, `pipapi` uses `DEV`, `pipfaker` uses `main`, and everything
else uses `PROD`.

## Viewing Current Configuration

```{r}
get_default_branch()
get_custom_branch()
get_current_branches()
```

## Modifying Configuration

```{r}
# Change the global default
set_default_branch("DEV")

# Override specific packages
set_custom_branch(pipdata = "main", pipapi = "DEV_v3")

# Verify
get_current_branches()
```

## Persisting Configuration Across Sessions

The options set by `set_default_branch()` and `set_custom_branch()` persist
for the current R session only. To make them permanent, add to your
`.Rprofile`:

```r
options(
  metapip.default_branch = "PROD",
  metapip.custom_branch = list(
    pipapi_branch = "DEV",
    wbpip_branch = "DEV",
    pipfaker_branch = "main"
  )
)
```