---
title: "metapip in package development"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{metapip in package development}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
 devtools::load_all(".")
# library(metapip)
```


## metapip: Managing PIP Ecosystem Packages for Development

The `metapip` package is designed to make it easy to manage all the packages in the PIP ecosystem. This is especially useful for package development, as the PIP packages depend on each other—most notably, like `pipfun`, which provides shared utilities. Coordinating branches and versions across these packages is essential for a smooth development workflow.

## Default and Custom Branches

To use the most recent version of a package, it's important to know which branch is considered the default for each package. By default, the branch is available with `get_default_branch()`, 

```{r}
get_default_branch()
```


and you can modify it with `set_default_branch()`. For example:

```r
set_default_branch("DEV")
```

However, not all packages' most recent versions are available in the same branch. Packages that do not use the default branch are tracked as "custom branches." You can see these with `get_custom_branch()`:

```{r}
get_custom_branch()
```

## Inspecting and Modifying Branch Assignments

To see all PIP ecosystem packages and their currently assigned branches, use `get_current_branches()`. To get the branch for a specific package, use `get_package_current_branch(package)`. For example:

```{r}
get_current_branches()
get_package_current_branch("pipdata")
```

If you need to change the working branch for any package, use `set_custom_branch()`. For example, to set the `pipdata` package to use the `main` branch and `pipapi` to use `DEV_v3`:

```{r}
set_custom_branch(pipdata = 'main', pipapi = 'DEV_v3')
```

## Listing Core Packages

To get a list of all core PIP packages, use:

```{r}
get_core_pagkages()
```

